\documentclass{article}
\usepackage{fullpage}
\usepackage{bbding}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage{color}

%\definecolor{green}{rgb}{0.2,0.7,0.4}
\definecolor{green}{RGB}{55, 100, 111}

\begin{document}
\thispagestyle{empty}
\begin{minipage}[c]{0.40\textwidth}
{\bfseries\Huge R}{\Huge aunaq}
{\bfseries\Huge G}{\Huge upta}

\hfill
\par
Phone: +91-9711071959\\
Email: raunaq2012@gmail.com\\
Website: http://www.raunaqgupta.in

\section*{{\color{green} Education}}
\begin{description}
\item
\par
{\bfseries B.Tech. in Computer Engineering (2009)}\\
Amity University, Noida\\
{\emph GPA: 8.31/10}

\item
\par
{\bfseries 12th Std. Senior Secondary (2004)}\\
Apeejay School, Pitampura\\
{\emph Percentage: 76 \%}

\item
{\bfseries 10th Std. Higher Secondary (2002)}\\
Apeejay School, Pitampura\\
{\emph Percentage: 81 \%}
\end{description}

\section*{{\color{green} IT \& Programming Skills}}

C/C++, Java, Python\\
HTML, Javascript, CSS\\
XML, JSON, XSLT\\
MySQL, Oracle, SQL Server\\
Windows, Linux(Debian), Solaris\\
Java/Swing, Qt, GTK\\
Gimp, 3Ds Max, Inkscape\\
Git, Hg, Clearcase, SVN\\
\TeX\ \LaTeX\

\section*{{\color{green} Languages}}

{\emph Hindi} (native speaker)\\
{\emph English} (professional proficiency)\\
{\emph French} (elementary proficiency)\\
{\emph Japanese} (elementary proficiency)

\section*{{\color{green} Activities}}

Certificate course in Psychology.\\
Certificate course in Japanese.\\
FOSS enthusiast. \\
Amity - Sun Microsystems member.\\
Crunchbang/Linux distro evangelist.\\
Intermediate Guitar player.\\
Shortlisted Candidate in HP Innovate '08.\\
"Jit Paul Scholarship" in Std. 12th.

\end{minipage}
\begin{minipage}[c]{0.6\textwidth}

\section*{{\color{green} Work Experience}}

\begin{description}

\item
{\bfseries Software Engineer $ \mid $ Aricent Group} \textit{April 2010 - Current}

Product development in C++ and Java for Intelligent Network
services involving INAP and SIP protocols.

{\bfseries FRC (Flexible Routing and Charging)}
\begin{itemize}\addtolength{\itemsep}{-0.4\baselineskip}
\item Intelligent Network (IN) telephony product.
\item Utilization of INAP protocols for call routing and charging. Works over all possible
telephony channels. User interface construction via Java and web based interfaces.
\item Technologies: C++, Java, Oracle, Solaris/Linux
\item Work as main developer on the product partaking in all stages from design to
development and testing.
\end{itemize}

\item
{\bfseries Software Engineer  $ \mid $ CPA Global} \textit{August 2009 - March 2010}

Data migration projects involving SQL and database systems, Process
enhancement and automation via development of tools in Java.

\item
{\bfseries Project Intern  $ \mid $ GEE Limited}  \textit{Summer '08}

Case-study on RFID based systems for smart-card implementations in the company, 
creation of a functional prototype for production.

\item
{\bfseries Project Intern  $ \mid $ Amity University} \textit{Summer '07}

Worked on AmityDB, a complete networked client-server based architecture system in
Java to provide Faculty with tools to manage schedules, student's information, and
providing an online bulletin board system.

\end{description}

\section*{{\color{green} Other Projects}}

\begin{description}

\item {\bfseries Multi-threaded, pluggable IRC bot}
\begin{itemize}\addtolength{\itemsep}{-0.4\baselineskip}
\item Developed in Python
\item Pluggable architecture for user developed modules, multi-threaded, user based privileges.
\end{itemize}

\item {\bfseries Desktop Screengrab + Uploader}
\begin{itemize}\addtolength{\itemsep}{-0.4\baselineskip}
\item Utilizes Qt/Qxt. Developed in C++.
\item Hotkey screengrab and automatic upload to a personal/public image hosting site like
imgur.com.
\end{itemize}

\item {\bfseries Fractal/Terrain Generator}
\begin{itemize}\addtolength{\itemsep}{-0.4\baselineskip}
\item Used Linux, C, OpenGL
\item Generator for Mira, Koch, Mandelbrot and Julian fractals.
\item Fully explorable 3D Terrain generation.
\end{itemize}

\end{description}

\end{minipage}

\end{document}
